\documentclass[margin,line,a4paper]{resume}
\usepackage[latin1]{inputenc}
\usepackage[english,french]{babel}
\usepackage[T1]{fontenc}
\usepackage{graphicx,wrapfig}
\usepackage{url}
\usepackage{textcomp}
\usepackage[colorlinks=true, a4paper=true, pdfstartview=FitV,
linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
%\pdfcompresslevel=9


\begin{document}{\sc \Large Short CV}
\begin{resume}
     \section{\mysidestyle Contact\\Information}%\vspace{2mm}
%   Shubhankar Majumdar \\
%   Date of birth: 1/11/1987 in Jabalpur, India \\
 Department of Electronics \& Communication, National Institute of Technology Meghalaya (NITM), \\
     Bijni Complex, Laitumkhrah, Shillong,  Meghalaya, India - 793003 \\
     Email: \href{mailto:shubuit@gmail.com}{shubuit@gmail.com} ; \href{mailto:shub@nitm.ac.in}{shub@nitm.ac.in};  \href{https://sites.google.com/site/shubhankarmajumdar1987/}{ Personal Website } \\
      \section{\mysidestyle Present Designation}
     Assistant Professor at National Institute of Technology, Meghalaya (NITM)
 \section{\mysidestyle Key Expertise } 
 Fabrication, Characterization, Simulation and Model III-N semiconductor devices; VLSI circuit; Embedded Design. 
	
           \section{\mysidestyle Highest Degree}
Doctor of Philosophy (PhD) in Micro-Electronics, Indian Institute of Technology, Kharagpur, 24$ ^{th} $ November 2016

\section{\mysidestyle Publications}
Total of >\textbf{30} referred \href{https://scholar.google.co.in/citations?user=PXDBASwAAAAJ&hl=en}{scientific publications}
 More than 45 citations giving an h-index of 4 (Web of Science \textsuperscript{TM}  )


%\section{\mysidestyle Presentations}
%2 Invited talks and numerous contributed talks and poster at international scientific conferences, more than 2 invited seminar talks.
\section{\mysidestyle Mentoring}
%0 supervised doctoral thesis; 0 supervised M.Tech thesis; 
\href{http://thesoil.in/team.php}{Incubated Startup} - Soil Agritech Pvt. Ltd. ;  3 supervised B.Tech Theses (3 Ongoing).
\section{\mysidestyle Teaching}
Taken lectures on various basic and advanced electronics and communication engineering courses since 2016. Deliver invited lecture at the several Faculty Development Program \& National seminars.
\section{\mysidestyle Management}
%\begin{itemize}
%	\item  \textbf{As Principal Investigator}
%	\begin{list2}
%		\item Project Title: Tensiometer based Automated IoT system for irrigation.\\
%		Sponsoring Agency:  Department of Science and Technology under Device Development Programme.\\
%		Status: Ongoing \\
%		Budget: 150000 INR. \\
%		Duration: 2 Years.
%	\end{list2}
%	
%	\item \textbf{As Co- Principal Investigator}
%	\begin{list2}
%		\item Project Title: Cloud-assisted Data Analytics based Real-Time Monitoring and Detection of Water Leakage in Transmission Pipelines using Wireless Sensor Network for Hilly Regions.\\
%		Sponsoring Agency:  Ministry of Earth Science under National Mission on Himalayan Studies (NHMS).\\
%		Budget: 4470880 INR. \\
%		Duration: 3 Years.
%	\end{list2}
%\end{itemize}
Presently, two projects of Department of Science and Technology under Device Development Programme (\textbf{150000 INR.}) and Ministry of Earth Science under National Mission on Himalayan Studies (NHMS) (\textbf{4470880 INR.}) are ongoing 
% Research group leader since 1/2006. Group of 15 people at the moment. 
\section{\mysidestyle Education International}
Coordinator and participant in international collaborative projects and networks, active research collaboration with more than 2 groups worldwide.
Member of the international programme, advisory or organizing committee of more than 10 international conferences
\section{\mysidestyle Reviewing}
Regular referee for \href{https://publons.com/author/1352342/shubhankar-majumdar}{numerous} journals, including IEEE, Elseiver, Springer, Wiley etc and conferences. Approximately 10 refereed articles / year. 

%  	  \section{\mysidestyle  Evaluation} \vspace{2mm}
%  Professorship, promotion, habilitation and PhD evaluation for several universities.\\
%  Project Evaluator like PRISM
  	 
%  	 \section{\mysidestyle Policy Making}      
%  	Member (2015 ? 2017) of the steering group, representing Finnish Universities
%  	excl. hospitals, for the overall renewal of the Finnish Law on radiation appointed by
%  	the Ministry of Social Affairs and Health (Finland). 

  	 \section{\mysidestyle Recognition}
  	 \begin{list2}
  	 	\item Received Marie Sklodowska-Curie Actions \href{https://www.dropbox.com/personal/my\%20documents/awards?preview=Seal+of+Excellence.pdf}{Seal of Excellence award} from European Commission in 2018.
  	 	\item Semifinalist for the Cisco Global Problem Solver Challenge in 2018.
  	 	\item Received \textbf{National Postdoctoral (NPDF) Fellowship} in 2017.
  	 	\item Received \textbf{Italian Fellowship for  Postdoctoral} in 2017.
  	 	\item \textbf{TI IICDC 2016} (\href{http://thesoil.in/team.php}{Website} | \href{https://www.youtube.com/watch?v=tNO64Y3uHVg&t=9s}{Technical Video} | \href{https://www.youtube.com/watch?v=CJbNIx8XI9c&t=28s}{Buisness Video})\\
  	 	Mentor of the Incubated Company --  Successfully become top 10 teams in Texas Instruments Inc. India Innovation Challenge Design Contest 2016 with over 11000 participants from 624 colleges of India. Got Incubation of   \textbf{INR 2500000/-} from Department of Science and Technology (DST), Texas Instruments, and anchored by NSRCEL of IIM Banglore for this project.   
  	 	
  	 	\item \textbf{ International Travel Grant} from Ministry of Human Resource and Development (MHRD) India for EMRS Fall Meeting, 2015, Warsaw Poland 
  	 	\item Received \textbf{ IIT KGP Institute Scholarship} in 2012 for pursuing PhD from MHRD, Government of India.
  	 	\item Received \textbf{GATE Scholarship} in 2010 for pursuing M.Tech from MHRD, Government of India.  
  	 	
  	 \end{list2}
  	
  	
 \end{resume}   
\end{document}
